### 2021-11-01 README.Rmd
Updated example descriptions

This example plots a vector x against each column of matrix z using the default `plot_type` of `ggmatplot()` - 'point'

@@

This example uses the iris dataset, with matrices x and y as shown below. The Sepal.Length is plotted against Sepal.Width and the Petal.Length is plotted against Petal.Width. Therefore the groups 'Column 1' and 'Column 2' can be interpreted as 'Sepal' and 'Petal' respectively.

@@

This example creates a line plot of vector x against the columns of matrix y. The plot is therefore grouped by the columns of vector y. Custom colors are assigned to each group using the `color` parameter, and the limits of the y axis are updated using the `ylim` parameter. Further, a ggplot theme is added on to the resultant ggplot object.

@@

This is a plot of the US personal expenditure over 5 categories and 5 years, and is a simple example of how wide format data can used with `ggmatplot()`. Note how the expenditure categories to be used on the x axis is used as vector x, and the expenditure values is used in wide format as matrix y - with its columns corresponding to the grouping structure.

>>>>

The first example plots a vector x against each column of matrix z using the default `plot_type` of `ggmatplot()` - 'point'

@@

The next example uses the iris dataset, with matrices x and y as shown below. The `Sepal.Length` is plotted against `Sepal.Width` and the `Petal.Length` is plotted against `Petal.Width`. Therefore the groups 'Column 1' and 'Column 2' can be interpreted as 'Sepal' and 'Petal' respectively.

@@

The next example creates a line plot of vector x against the columns of matrix y. Although the lines would be represented using different colors by default, the `color` parameter allows custom colors to be assigned to them.
The following plot assigns custom colors to the lines, and the limits of the y axis are updated using the `ylim` parameter. Further, a ggplot theme is added on to the resultant ggplot object.

@@

Next is plot of the US personal expenditure over 5 categories and 5 years, and is a simple example of how wide format data can used with `ggmatplot()`. Note how the expenditure categories to be used on the x axis is used as vector x, and the expenditure values is used in wide format as matrix y - with its columns corresponding to the grouping structure.
